---
title: "first_R"
author: "bugkiller"
date: "7 February 2017"
output: html_document
---

##LOADING OF HONE DATA  
```{r}
Price.House=read.csv("home_data.csv")
names(Price.House)
Price.House=Price.House[,-1]
library("caret")
trainIndex<-createDataPartition(Price.House$price,p=.70,list = FALSE)
Price.HouseTrain<-Price.House[trainIndex,]
head(Price.HouseTrain)
str(Price.HouseTrain)
summary(Price.HouseTrain)
Price.HouseTest<-Price.House[-trainIndex,]
head(Price.HouseTest)
summary(Price.HouseTest)
cor(Price.HouseTrain[,-c(1,2)])
library("PerformanceAnalytics")
my_data<-Price.HouseTrain[,-c(1,2)]
chart.Correlation(my_data, histogram=TRUE,pch=19)
library(corrplot)
corrplot(my_data,type="upper",order="hclust",
         tl.cal="black",tl.srt=45,addrect=2)

##Running a model
```{r }
#options(show.signif.stars=F)
Simple.Reg.Model=lm(price ~.,data=Price.HouseTrain)
summary(Simple.Reg.Model)
names(Simple.Reg.Model)
confint(Simple.Reg.Model,level = 0.95)
##goodness of fit
```{r}
anova(Simple.Reg.model)
```
##plotting regression diagnostics
```{r echo=FALSE}
par(mfrow=c(2,2))
plot(Simple.Reg.model)
```

#predicting model on test data and checking accuracy
```{r}
test.pred<-predict(Simple.Reg.model,price.HouseTest)
actuals_preds<-data.frame(cbind(actuals=price.HouseTest$price,predicted=test.pred))
head(actuals_preds)
```
##Testing Accuracy on Test set
```{r}
test.y=Price.HouseTest$price
ss.total=sum((test.y - mean(test.y))^2)
ss.residual=sum((test.y - test.pred)^2)
ss.regression=sum((test.pred-mean(test.y))^2)
ss.total-(ss.regression+ss.residual)
##fraction of variability explained by the model
ss.regression/ss.total*100
R_SquareTrain=summary(Simple.Reg.Model)$r.squared*10
R_SquareTrain
